Robot Team III: Scotty Strikes Back

### 2024-04-23 paper/paper.tex
Updates from Overleaf

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
Unmanned Aerial Vehicles (UAVs) equipped with hyperspectral imagers have emerged as a pivotal technology for the characterization of inland water bodies. The high spectral and spatial resolutions of these systems enable the retrieval of a plethora of optically-active water quality parameters via band ratio algorithms and machine learning methods. However, fitting and validating these models requires access to sufficient quantities of in situ reference data which are time-consuming and expensive to obtain. 
In this study, we demonstrate how the Generative Topographic Mapping (GTM), a Bayesian realisation of the Self Organizing Map (SOM), can be effectively used to enable unsupervised classification and nonlinear endmember extraction of UAV acquired hyperspectral imagery.

to enable fully unsupervised classification UAV acquired hyperspectral imagery.

The methods is fully Bayesian, providing an attractive method for the unsupervised classification of hyperspectral imagery.

- generative topographic mapping (GTM) as an efficient unsupervised method 
- additionally the GTM can be used to perform nonlinear endmember extraction
- We demonstrate the abilities of this approach using hyperspectral imagery collected at a pond in Montague, North Texas.
- First, we apply the GTM to perform an unsupervised classification for all water pixels. 
    - benefit: GTM classes maintain topological relationships in the latent space resulting in a smooth relationship between the obtained classes...
    - ... revealing the small-scale spatial variability within the pond
- Second, we utilize the GTM to identify reflectance spectra corresponding to specific features. 
- Using these extracted features, we are able to map the extent of algae in the pond in addition to the time evolution of a rhodamine dye tracer. 
- This approach demonstrates the value of unsupervised techniques coupled with UAV-born hyperspectral imaging for rapid water quality assessment.
}

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
Unmanned Aerial Vehicles (UAVs) equipped with hyperspectral imagers have emerged as a pivotal technology for the characterization of inland water bodies. The high spectral and spatial resolutions of these systems enable the retrieval of a plethora of optically-active water quality parameters via band ratio algorithms and machine learning methods. However, fitting and validating these models requires access to sufficient quantities of in situ reference data which are time-consuming and expensive to obtain. 
In this study, we demonstrate how the Generative Topographic Mapping (GTM), a Bayesian realisation of the Self Organizing Map (SOM), can be effectively used to enable unsupervised classification and nonlinear endmember extraction of UAV acquired hyperspectral imagery. Using imagery collected across a North Texas Pond, we demonstrate how th
- to enable fully unsupervised classification UAV acquired hyperspectral imagery.
-The methods is fully Bayesian, providing an attractive method for the unsupervised classification of hyperspectral imagery. 
- generative topographic mapping (GTM) as an efficient unsupervised method 
- additionally the GTM can be used to perform nonlinear endmember extraction
- We demonstrate the abilities of this approach using hyperspectral imagery collected at a pond in Montague, North Texas.
- First, we apply the GTM to perform an unsupervised classification for all water pixels. 
    - benefit: GTM classes maintain topological relationships in the latent space resulting in a smooth relationship between the obtained classes...
    - ... revealing the small-scale spatial variability within the pond
- Second, we utilize the GTM to identify reflectance spectra corresponding to specific features. 
- Using these extracted features, we are able to map the extent of algae in the pond in addition to the time evolution of a rhodamine dye tracer. 
- This approach demonstrates the value of unsupervised techniques coupled with UAV-born hyperspectral imaging for rapid water quality assessment.
}
